
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE)
```

## Objective
You work for Motor Trend, a magazine about the automobile industry. Looking at a data set of a collection of cars, they are interested in exploring the relationship between a set of variables and miles per gallon (MPG) (outcome). 

They are particularly interested in the following two questions:

- “Is an automatic or manual transmission better for MPG”
- "Quantify the MPG difference between automatic and manual transmissions"

```{r cars}
library(tidyr)
library(ggplot2)

#load dataset
data(mtcars)

# overview mtcars
head(mtcars)
```

## EDA phase

We will focus on transmission relationship with other variables

```{r}
# check direct relation between mpg and transmission type, ignoring other factors
mtcars %>%
  ggplot(aes(am,mpg))+
  geom_point(aes(colour = factor(am)),na.rm = TRUE)+
  geom_smooth(method = "lm", se = FALSE) +
  ggtitle("transmission-Mpg direct relation (0=automatic, 1=Manual)")

# select couple of variables and check relationship
# check relation between mpg and cyl, split by transmission type
mtcars %>%
  ggplot(aes(cyl,mpg))+
  geom_point(aes(colour = factor(cyl)),na.rm = TRUE)+
  facet_grid(cols = vars(as.factor(am)))+
  geom_smooth(method = "lm", se = FALSE) +
  ggtitle("Cyl-Mpg relation split by transmission type (0=automatic, 1=Manual)")

# check relation between mpg and wt, split by transmission type
mtcars %>%
  ggplot(aes(wt,mpg))+
  geom_point(aes(colour = factor(wt)),na.rm = TRUE)+
  facet_grid(cols = vars(as.factor(am)))+
  geom_smooth(method = "lm", se = FALSE) +
  ggtitle("Weight-Mpg relation split by transmission type (0=automatic, 1=Manual)")

# check relation between mpg and vs, split by transmission type
mtcars %>%
  ggplot(aes(vs,mpg))+
  geom_point(aes(colour = factor(vs)),na.rm = TRUE)+
  facet_grid(cols = vars(as.factor(am)))+
  geom_smooth(method = "lm", se = FALSE) +
  ggtitle("VS-Mpg relation split by transmission type (0=automatic, 1=Manual)")

```

## explore linear models phase

``` {r}
# fit1 is simple, will be only between mpg and transmission
fit1 <- lm(mpg~am-1 , data = mtcars)
summary(fit1)$coefficients


# fit2 is multi-model between mpg & all variables 
fit2 <- glm(mpg~. , data = mtcars)
summary(fit2)$coefficients
# plot model
par(mfrow = c(2, 2))
plot(fit2)

# will add one variable at a time to mpg and transmission
fit3 <- lm(mpg~cyl+am , data = mtcars)
summary(fit3)$coefficients
# plot model
par(mfrow = c(2, 2))
plot(fit3)

fit4 <- lm(mpg~wt+am , data = mtcars)
summary(fit4)$coefficients
# plot model
par(mfrow = c(2, 2))
plot(fit4)

fit5 <- lm(mpg~vs+am , data = mtcars)
summary(fit5)$coefficients
# plot model
par(mfrow = c(2, 2))
plot(fit5)
```

## Summary

- Automatic Transmission has better impact on mpg
- Residuals show that considering other variables in the process of fitting a model is much better than considering only mpg & am